Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Update interpretations for soruce and target WCRQA

### Syria as Source and Target
WCRQA of recurrence rate on the source and target filtered data remained
largely the same for count of all events and social cohesion, suggesting
that large numbers on a given day will be reflective of increased levels
of social cohesion. DET showed more frequent above-chance metrics
for windows 39 and up, suggesting that the inclusion of externally
directed events lead to higher event counts during these days and then
was more reflective of the level of social cohesion on Twitter.

WCRQA metrics for positive-only and negative-only event counts with 
social cohesion remained largely the same for
RR and DET as the source-only data. This may support the ideas suggested
in the CRQA section, but again, only future work including the *content*
of those tweets can directly speak to that explanation.

>>>>

### Syria as Source and Target
WCRQA on the source-and-target-filtered data showed similar
patterns of RR between the count of all events and social cohesion
(as observed in the target-only data), 
though the values increased. This suggests
that large numbers on a given day match increased levels
of social cohesion online. However, the results for DET changed:
While the majority of statistically significant DET windows
occurred toward the end of the observation period for target-only
data (creating a positive trendline), the source-and-target data
showed a negative trendline for DET.

The divergences in the all-event count data for these two
datasets underscores the differences
between RR and DET. As noted earlier, DET captures *trajectories*---in
this case, similar to the impact of actions and social cohesion
carrying across time. The same number of points (RR) can fall in
different patterns (DET), providing important information
about the structure of the system in question.

WCRQA metrics for positive-only event counts with social cohesion showed 
similar patterns in RR and DET as the target-only data, but the precise
values of DET and RR were diminished. This may support the ideas suggested
in the CRQA section, but again, only future work including the *content*
of those tweets can directly speak to that explanation.

Finally, the coupling between negative-only event counts and
social cohesion also remained relatively similar but demonstrated some 
important differences. First, we see a greater number of windows at
above-chance levels for RR, including an interesting spike around window
32 that suggests a negative externally focused action taken by Syria
prompted a sharp rise in social cohesion. (This would not have been
captured by the target-only dataset.) Second---like with the all-event
data---we see different structuring of the data through differences
in the patterns of DET; above-chance DET only occurrs within the middle
of the observation period, around a time of increased strive (as
noted above).
